Considering scale in multilayer animal social networks

### 2020-06-20 paper/manuscript.Rmd
last foraging

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (forage, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and foraging layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.

>>>>

<!-- Figure: metrics by social scale -->
(ref:socres) Varying scale in social distance threshold. For each social distance threshold (100 - 1000 m by steps of 100 m), multilayer networks were constructed of caribou social associations (n = `r DT[, uniqueN(get(idcol))]` females) on Fogo Island, Newfoundland between `r DT[, format(min(datetime), '%F')]` and `r DT[, format(max(datetime), '%F')]` across three habitat classes (foraging, forest, and open). Graph strength (mean of individuals in bold) showed a sharp increase between 5 m and 100 m for all habitat classes. After 100 m, graph strength continued to increase at a slower rate. Open and foraging layers showed higher variation in graph strength between individuals while the forest layer had less variation and lower mean graph strength.
